ms_borrador

### 2018-01-23 man/ms_tables/t_huber_res_bai.Rmd
update tables

**Table S2.** Estimadores huber resiliences BAI

>>>>

**Table S2.** Robust measures of central tendency of resilience indices for tree-growth (BAI) groupped by drought events, site and interaction. Measures of central tendency are M-estimators based on Huber's Psi (see material and methods). 95 % confidence intervals using 3000 bootstrap are included in parentheses.

### 2018-01-23 man/ms_tables/t_huber_res_evi.Rmd
update tables

**Table S1.** Estimadores huber resiliences EVI

>>>>

**Table S1.** Robust measures of central tendency of resilience indices for greenness (EVI) groupped by drought events, site and interaction. Measures of central tendency are M-estimators based on Huber's Psi (see material and methods). 95 % confidence intervals using 3000 bootstrap are included in parentheses.

### 2018-01-23 man/ms_tables/t_robust_anovas.Rmd
update tables

```{r, echo=FALSE, include = FALSE}
### Table R1_evi
df <- read.csv(here("/out/anovas_resilience/huber_evi", "trimmed_anovas.csv"), header = TRUE)
names(df) <- c('factores', 'F', 'p', 'variables')

dff <- df %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drougth event", 
                           "disturb_year:site" = "Drougth event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drougth event", "Site", "Drougth event X Site")))

colnames(dff) <- c("", "rc\nF", "rc\np", "rrs\nF", "rrs\np", "rs\nF", "rs\np", "rt\nF", "rt\np")
pander(dff,
             round=c(0,2,3,2,3,2,3,2,3),
             digits=c(0,5,4,5,4,5,4,5,4),
             keep.line.breaks = TRUE
             )
dff

```

```{r, echo=FALSE, include = FALSE}
### Table R1_evi sin rrs 
df <- read.csv(here("/out/anovas_resilience/huber_evi", "trimmed_anovas.csv"), header = TRUE)
names(df) <- c('factores', 'F', 'p', 'variables')

dff <- df %>% 
  filter(variables != "rrs") %>% 
  gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drougth event", 
                           "disturb_year:site" = "Drougth event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drougth event", "Site", "Drougth event X Site")))

# knitr::kable(dff, 
#       col.names = c("", "F", "p", "F", "p", "F", "p", "F", "p"),
#       digits=c(0,2,3,2,3,2,3,2,3))

dff_evi <- dff %>% mutate(target = 'EVI')

colnames(dff) <- c("", "rc\nF", "rc\np", "rs\nF", "rs\np", "rt\nF", "rt\np")
pander(dff,
             round=c(0,2,3,2,3,2,3,2,3),
             digits=c(0,5,4,5,4,5,4,5,4),
             keep.line.breaks = TRUE
             )
dff

```

```{r, echo=FALSE, include = FALSE}

### Table R1_bai
df <- read.csv(here("/out/anovas_resilience/huber_bai", "trimmed_anovas.csv"), header = TRUE)
names(df) <- c('factores', 'F', 'p', 'variables')

dff <- df %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drougth event", 
                           "disturb_year:site" = "Drougth event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drougth event", "Site", "Drougth event X Site")))

# knitr::kable(dff, 
#       col.names = c("", "F", "p", "F", "p", "F", "p", "F", "p"),
#       digits=c(0,2,3,2,3,2,3,2,3))

colnames(dff) <- c("", "rc\nF", "rc\np", "rrs\nF", "rrs\np", "rs\nF", "rs\np", "rt\nF", "rt\np")
pander(dff,
             round=c(0,2,3,2,3,2,3,2,3),
             digits=c(0,5,4,5,4,5,4,5,4),
             keep.line.breaks = TRUE
             )
dff

```

```{r, echo=FALSE, include = FALSE}
### Table R1_bai sin rrs 
df <- read.csv(here("/out/anovas_resilience/huber_bai", "trimmed_anovas.csv"), header = TRUE)
names(df) <- c('factores', 'F', 'p', 'variables')

dff <- df %>% 
  filter(variables != "rrs") %>% 
  gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drougth event", 
                           "disturb_year:site" = "Drougth event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drougth event", "Site", "Drougth event X Site")))

dff_bai <- dff %>% mutate(target = 'BAI')

# knitr::kable(dff, 
#       col.names = c("", "F", "p", "F", "p", "F", "p", "F", "p"),
#       digits=c(0,2,3,2,3,2,3,2,3))

colnames(dff) <- c("", "rc\nF", "rc\np", "rs\nF", "rs\np", "rt\nF", "rt\np")
pander(dff,
             round=c(0,2,3,2,3,2,3,2,3),
             digits=c(0,5,4,5,4,5,4,5,4),
             keep.line.breaks = TRUE
             )
dff

```

```{r, echo=FALSE}
# table 2 (r1)
dffs <- dff_bai %>% bind_rows(dff_evi) %>% dplyr::select(8,1:7)

# write.csv(dffs, here("/out/anovas_resilience", "trimmed_anovas_joined.csv"), row.names = FALSE)

# kable(dffs, format = "latex", booktabs = T,
#       col.names = c("", "F", "p", "F", "p", "F", "p", "variable"),
#       digits=c(0,2,3,2,3,2,3,2,3,0)) %>% 
#   kable_styling(font_size = 8) %>% 
#   add_header_above(c("", "rc" = 2, "rs" = 2, "rt" = 2))

dffs <- dffs %>% 
  mutate_at(c(3,5,7), round, 2) %>%
  mutate_at(c(4,6,8), round, 3)

colnames(dffs) <- c("variable", "factores", "rc\nF", "rc\np", "rs\nF", "rs\np", "rt\nF", "rt\np")
pander(dffs)
```

>>>>

```{r, echo=FALSE, include = FALSE}
### Table R1_evi
evi <- read.csv(here("/out/anovas_resilience/huber_evi", "trimmed_anovas.csv"), header = TRUE)
names(evi) <- c('factores', 'F', 'p', 'variables')

dff_evi <- evi %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drougth event", 
                           "disturb_year:site" = "Drougth event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drougth event", "Site", "Drougth event X Site"))) %>% 
  mutate_at(c(2,4,6,8), round, 2) %>% 
  mutate_at(c(3,5,7,9), round, 3) %>% 
  mutate(variable = 'evi')

bai <- read.csv(here("/out/anovas_resilience/huber_bai", "trimmed_anovas.csv"), header = TRUE)
names(bai) <- c('factores', 'F', 'p', 'variables')

dff_bai <- bai %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drougth event", 
                           "disturb_year:site" = "Drougth event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drougth event", "Site", "Drougth event X Site"))) %>% 
  mutate_at(c(2,4,6,8), round, 2) %>% 
  mutate_at(c(3,5,7,9), round, 3) %>% 
  mutate(variable = 'bai')

dff <- dff_evi %>% 
  bind_rows(dff_bai) %>% 
  dplyr::select(-rrs_F, -rrs_p) %>% 
  dplyr::select(variable, factores, rt_F, rt_p, rc_F, rc_p, rs_F, rs_p)
```

```{r, echo=FALSE}
colnames(dff) <- c("variable", "factores", "rt\nF", "rt\np", "rc\nF", "rc\np", "rs\nF", "rs\np")
pander(dff)
```
